---
title: "01_Analyses_Study5"
author: SSK
format: 
  html:
    self-contained: true
    embed-resources: true
    toc: true
editor: visual
editor_options: 
  chunk_output_type: console
---

# Description

These analyses were conducted for Chapter 1 Study 5 of my dissertation. This study is currently under review at *Journal of Experimental Psychology - Applied*.

## Abstract

In the healthcare context, patient socioeconomic status (SES) informs how patients are perceived and treated, contributing to downstream health disparities. The current experimental research reveals the nature of such interpersonal challenges for low-SES patients. Across four experiments (total N = 1142), participants engaged in a series of mock telehealth visits with a patient who failed to follow treatment recommendations twice and were therefore noncompliant. Evidence suggests that after repeated noncompliance, low-SES patients are perceived disproportionately more harshly, as more lazy, less honest, and as exaggerating their pain more, than high-SES patients exhibiting the same behavior. These worsening perceptions of the patient predict lower intentions to invest in care for the patient in the future. Furthermore, low-SES patients receive less intense treatment than high-SES patients, regardless of patterns of noncompliance. Our findings for low-SES bias in the healthcare context are not moderated by patient race or gender. Internal meta-analyses provide additional support for these findings. This low-SES bias in the healthcare context suggests that biased perceptions of patients by their SES plays a pivotal role in social class health disparities.

::: {style="margin-left: 2em;"}
*Keywords:* bias, stereotypes, socioeconomic status, healthcare, health
:::

# Set-up

```{r, packages}
#| warning: false
#| message: false
#| code-fold: true
# loading packages
library(psych)
library(ggplot2)
library(effsize)
library(dplyr)
library(kableExtra)
library(GPArotation)
library(stats)
library(plyr)
library(psych)
library(tidyverse)
library("Hmisc")
library(forcats)
library(grid)
library(ggcorrplot)
library(corrplot)
library(gridExtra)
library("ggdark")
library(broom)
library("effects")
library(lsmeans)
library(emmeans)
library(diagram)
library(pwr)
library(dplyr)
library(tidyr)
library(nlme)
library(rstatix)
library(multcomp)
library(lme4)
library(lmerTest)
library(cowplot)
library(report)
library(sjPlot)
library(lavaan)
library(lavaan)
library("corrplot")
library(dplyr)
library(GPArotation)
library(psych)
library(RcmdrMisc)
library(plot3D)
library(effectsize)
library(sjmisc)
library(rstatix)
library(gtsummary)
```

```{r, ggplot_functions}
#| warning: false
#| message: false
#| code-fold: true
# creating ggplot functions 
theme_perez <- function() {
    ggplot2::theme_bw() +
    ggplot2::theme(
      axis.text = element_text(colour = "black",  family = "Times New Roman", size = 12),
    axis.title = element_text(colour = "black", family = "Times New Roman", size = 13),
    legend.title = element_text(colour = "black", family = "Times New Roman", size = 13),
    legend.text = element_text(colour = "black", family = "Times New Roman", size = 12),
    plot.title = element_text(colour = "black", family = "Times New Roman", size = 13),
    plot.subtitle = element_text(colour = "black", family = "Times New Roman", size = 13),
    strip.text = element_text(colour = "black", family = "Times New Roman", size = 13))
}

horzi_theme <- theme(    #   remove the gray background
  panel.background    = element_rect( size=.1, colour="black", fill="white") ,
  #   make the major gridlines light gray and thin
  panel.grid.major.y  = element_line( size=.1, colour="#666666" ) ,
  #   suppress the vertical grid lines
  panel.grid.major.x  = element_blank() ,
  #   suppress the minor grid lines
  panel.grid.minor    = element_blank() ,
  #   add axes
  axis.line           = element_line( size=.2 , colour="#666666" ),
  #   adjust the axis ticks
  axis.ticks          = element_line( size=.1 , colour="#666666" ),
  #   move the y-axis over to the left
  #axis.title.y        = element_text( angle=90, vjust=.5, hjust=.5 ),
  #   increase margin moved-over y-axis label fits
  # plot.margin = unit( c(.5,.25,.25,.5) , "in") ,
  title = element_text(  size=12 ) ,
  axis.title.x = element_text( size=12 ) ,
  axis.title.y = element_text( size=12 ) ,
  axis.text.x = element_text( size=12 ) ,
  axis.text.y = element_text( size=12 )
)

horzi <- horzi_theme

stat_sum_df <- function(fun, geom="crossbar", ...) {
  stat_summary(fun.data=fun, colour="black", geom=geom, width=.5,  ...)
}

# define the dodge object for equivalent error bar and geom_bar
dodge <- position_dodge(width=0.9)

# define a geom_bar
bars <- geom_bar(stat="summary", fun.y="mean", position="dodge")
```

```{r, data}
#| code-fold: true
# importing data 
data <- read.csv("Data_Processed_Study5.csv")
data_wide <- read.csv("Data_Processed_Study5-Wide.csv")
```

## *n*s

```{r}
#| code-fold: true
kable(table(data$study), col.names = c("Study","n"))

kable(table(data_wide$conditionSES), col.names = c("SES Condition", "n"))
```

# Reported Outcomes

::: {.panel-tabset}

#### Patient Laziness

```{r}
#| warning: false
#| code-fold: true
ggplot(data=data, aes(as.factor(strike), lazy, fill=conditionSES)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_se", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  theme_perez() +
  scale_fill_grey() +
  xlab("Noncompliance Incident / 'Strike'") +
  ylab("Perceived Patient Laziness") +
  guides(fill=guide_legend(title="Patient SES")) +
  theme(legend.position="bottom") 

modLazy <- lmer(lazy ~ conditionSES * strike + ladder_Self + income_Self + ed_Own + study + conditionRace + (1|ResponseId), data=data, na.action=na.omit)

kable(anova(modLazy), caption = "Model Output")

effectsize::eta_squared(modLazy, partial=T) %>% 
  select(1:2) %>% 
  kable(caption = "Effect Sizes")

kable(emmeans(modLazy, pairwise ~ conditionSES * strike)$contrasts, caption = "Contrasts")
```

#### Patient Honesty

```{r, echo=F, warning=F, message=F}
#| warning: false
#| code-fold: true
ggplot(data=data, aes(factor(strike), honest, fill=conditionSES)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  scale_y_continuous(breaks = c(1:5)) +
  stat_sum_df("mean_se", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  labs(x = "Noncompliance Incident / 'Strike'",
       y = "Perceived Patient Honesty",
       fill = "Patient SES") +
  theme_perez() +
  scale_fill_grey() +
  theme(legend.position="bottom") 

modHon <- lmer(honest ~ conditionSES * strike + ladder_Self + income_Self + ed_Own + study + conditionRace + (1|ResponseId), data=data, na.action=na.omit)

kable(anova(modHon), caption = "Model Output")

effectsize::eta_squared(modHon, partial=T) %>% 
  select(1:2) %>% 
  kable(caption = "Effect Sizes")

kable(emmeans(modHon, pairwise ~ conditionSES * strike)$contrasts, caption = "Contrasts")
```

#### Patient Exaggerating Pain

```{r, echo=F, warning=F, message=F}
#| warning: false
#| code-fold: true
ggplot(data=data, aes(factor(strike), exaggerate, fill=conditionSES)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  scale_y_continuous(breaks = c(1:5)) +
  stat_sum_df("mean_se", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  labs(x = "Noncompliance Incident / 'Strike'",
       y = "Perceived Patient Pain Exaggeration",
       fill = "Patient SES") +
  theme_perez() +
  scale_fill_grey() +
  theme(legend.position="bottom")

modExag <- lmer(exaggerate ~ conditionSES * strike + ladder_Self + income_Self + ed_Own + study + conditionRace + (1|ResponseId), data=data, na.action=na.omit)

kable(anova(modExag), caption = "Model Output") 

effectsize::eta_squared(modExag, partial=T) %>% 
  select(1:2) %>% 
  kable(caption = "Effect Sizes")

kable(emmeans(modExag, pairwise ~ conditionSES * strike)$contrasts, caption = "Contrasts")
```

#### Feel Like Giving Up on Patient

```{r, echo=F, warning=F, message=F}
#| warning: false
#| code-fold: true
modGiveUp <- lmer(givingUp ~ conditionSES * strike + ladder_Self + income_Self + ed_Own + study + conditionRace + (1|ResponseId), data=data, na.action=na.omit)

kable(anova(modGiveUp), caption = "Model Output")

effectsize::eta_squared(modGiveUp, partial=T) %>% 
  select(1:2) %>% 
  kable(caption = "Effect Sizes")
```

#### Pred. by Change in Perceptions

::: {.panel-tabset}
#### Change in Patient Laziness
```{r}
#| warning: false
#| code-fold: true
mod <- lm(givingUp_2 ~ lazy_2 + conditionSES + lazy_1 + income_Self + ladder_Self + ed_Own + conditionRace + study, data_wide)

tab_model(mod)

effectsize::eta_squared(mod, partial=T) %>% 
  select(1:2) %>% 
  kable(caption = "Effect Sizes")

data_wide$lazy_change <- data_wide$lazy_2 - data_wide$lazy_1
data_wide$lazyIncrease <- case_when(data_wide$lazy_change >= 1 ~ "1",
                              data_wide$lazy_change == 0 ~ "0",
                              TRUE ~ "-1")

ggplot(data_wide, aes(lazy_change, givingUp_2)) +
  geom_jitter(aes(colour=factor(lazyIncrease)), alpha=0.5) +
  stat_smooth(method="lm", color="#003f5c") +
  scale_x_continuous(breaks=c(-4:4)) +
  labs(x = "Change in Perceived Patient Laziness from Strike 1 to Strike 2",
       y = "Desire to 'Give Up' after Strike 2",
       title = "\U0394 Laziness \U2192 Giving Up",
       subtitle = "Meta-Analysis") +
  guides(colour=guide_legend(title="Direction\nof Change")) +
  scale_color_manual(values=c("#B3DFFF", "#768fe8", "#0a7cfc"), labels=c("Decrease", "No Change", "Increase")) +
  theme_perez() +
  theme(legend.position="bottom")

ggplot(data_wide, aes(lazy_change, givingUp_2, fill=conditionSES)) +
  geom_jitter() +
  stat_smooth(method="lm") +
  scale_x_continuous(breaks=c(-3:4)) +
  labs(x = "Change in Perceived Patient Laziness from Strike 1 to Strike 2",
       y = "Desire to 'Give Up' after Strike 2") +
  theme_perez() +
  theme(legend.position="bottom")
```

#### Change in Patient Honesty
```{r}
#| warning: false
#| code-fold: true
mod <- lm(givingUp_2 ~ honest_2 + conditionSES + honest_1 + income_Self + ladder_Self + ed_Own + conditionRace + study, data_wide)

tab_model(mod)
effectsize::eta_squared(mod, partial=T) %>% 
  select(1:2) %>% 
  kable(caption = "Effect Sizes")

# settings for plots
data_wide$honest_change <- data_wide$honest_1 - data_wide$honest_2

data_wide$honIncrease <- case_when(data_wide$honest_change >= 1 ~ "1",
                              data_wide$honest_change == 0 ~ "0",
                              TRUE ~ "-1")

ggplot(data_wide, aes(honest_change, givingUp_2)) +
  geom_jitter(aes(colour=factor(honIncrease)), alpha=0.5) +
  stat_smooth(method="lm", color="#003f5c") +
  scale_x_continuous(breaks=c(-4:4)) +
  labs(x = "Change in Perceived Patient Honesty from Strike 1 to Strike 2",
       y = "Desire to 'Give Up' after Strike 2",
       title = "\U0394 Honesty \U2192 Giving Up",
       subtitle = "Meta-Analysis") +
  guides(colour=guide_legend(title="Direction\nof Change")) +
  scale_color_manual(values=c("#B3DFFF", "#768fe8", "#0a7cfc"), labels=c("Decrease", "No Change", "Increase")) +
  theme_perez() +
  theme(legend.position="bottom")
```

#### Change in Patient Pain Exaggeration
```{r}
#| warning: false
#| code-fold: true
mod <- lm(givingUp_2 ~ exaggerate_2 * conditionSES + exaggerate_1 + income_Self + ladder_Self + ed_Own + conditionRace + study, data_wide)

tab_model(mod)

effectsize::eta_squared(mod, partial=T) %>% 
  select(1:2) %>% 
  kable(caption = "Effect Sizes")

data_wide$exag_change <- data_wide$exaggerate_2 - data_wide$exaggerate_1

data_wide$exagIncrease <- case_when(data_wide$exag_change >= 1 ~ "1",
                              data_wide$exag_change == 0 ~ "0",
                              TRUE ~ "-1")

ggplot(data_wide, aes(exag_change, givingUp_2)) +
  geom_jitter(aes(colour=factor(exagIncrease)), alpha=0.5) +
  stat_smooth(method="lm", color="#003f5c") +
  scale_x_continuous(breaks=c(-4:4)) +
  labs(x = "Change in Perceived Pain Exaggeration from Strike 1 to Strike 2",
       y = "Desire to 'Give Up' after Strike 2",
       title = "\U0394 Pain Exaggeration \U2192 Giving Up",
       subtitle = "Meta-Analysis") +
  guides(colour=guide_legend(title="Direction\nof Change")) +
  scale_color_manual(values=c("#B3DFFF", "#768fe8", "#0a7cfc"), labels=c("Decrease", "No Change", "Increase")) +
  theme_perez() +
  theme(legend.position="bottom")
```

:::

#### Treatment Decisions

```{r}
#| warning: false
#| code-fold: true
ggplot(data=data, aes(conditionSES, treatAvg, fill=factor(strike))) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:4)) +
  scale_y_continuous(breaks=c(1:4), labels=c("1-Lowest\nTreatment\nIntensity","2","3","4-Highest\nTreatment\nIntensity")) +
  xlab("Patient SES") +
  ylab("Treatment Intensity") +
  theme_perez() +
  scale_fill_grey() +
  guides(fill=guide_legend(title="Noncompliance Incident / 'Strike'")) +
  theme(legend.position="bottom") +
  theme(axis.text.x=element_text(angle=15, vjust=.8, hjust=0.8))

modTreat <- lmer(treatAvg ~ conditionSES + strike + income_Self + ladder_Self + ed_Own + study + conditionRace + (1|ResponseId), data=data)

anova(modTreat)

effectsize::eta_squared(modTreat, partial=T) %>% 
  select(1:2) %>% 
  kable(caption = "Effect Sizes")

emmeans(modTreat, pairwise ~ conditionSES)
emmeans(modTreat, pairwise ~ strike)
```

:::

# Patient SES Manipulation Check

::: {.panel-tabset}

#### Perceived Patient Subjective SES (Ladder)
```{r}
#| warning: false
#| code-fold: true
tab_model(t.test(data_wide$ladder_Patient ~ data_wide$SES))
```

#### Perceived Patient Objective SES (Income)
```{r}
#| warning: false
#| code-fold: true
tab_model(t.test(data_wide$income_Patient ~ data_wide$SES))
```

#### Perceived Patient Education Level
```{r}
#| warning: false
#| code-fold: true
tab_model(t.test(data_wide$ed_Patient ~ data_wide$SES))
```

::: 

# Participant Demographics

::: {.panel-tabset}

#### Subjective SES (Ladder)
```{r}
#| warning: false
#| code-fold: true
hist(data_wide$ladder_Self, xlab = "Ladder Position", main = "Subjective SES (Ladder)")
kable(psych::describe(data_wide$ladder_Self), caption = "Subjective SES (Ladder)", row.names = NA)
```

#### Objective SES (Income)
```{r}
#| warning: false
#| code-fold: true
hist(data_wide$income_Self, xlab = "Income", main = "Objective SES (Income)")
kable(psych::describe(data_wide$income_Self), row.names = NA, caption = "Objective SES (Income)") 
```

#### Education Level
```{r}
#| warning: false
#| code-fold: true
kable(table(factor(data_wide$ed_Own, labels = c("< HS", "HS", "College", "Post-grad"))), col.names = c("Education Level", "n"), caption = "Objective SES (Education Level)", row.names = NA)
```

#### Race
```{r}
#| warning: false
#| code-fold: true
kable(table(factor(data_wide$race_Self, labels = c("White/Caucasian", "Asian/Asian-American", "Black/African American", "Hispanic/Latinx", "East Asian/East Asian-American", "Multiracial", "Other"))), col.names = c("Race", "n"), caption = "Race", row.names = NA) 
```

#### Gender
```{r}
#| warning: false
#| code-fold: true
kable(table(data_wide$gender_Self), col.names = c("Gender", "n"), caption = "Gender", row.names = NA) 
```
:::

# Additional Outcomes

::: {.callout-note collapse="true"}
## Patient Motivation

```{r}
#| warning: false
#| code-fold: true
ggplot(data=data, aes(conditionSES, motivated, fill=as.factor(strike))) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  theme_perez() +
  scale_fill_grey() +
  xlab("Patient SES") +
  ylab("Perception of Patient Motivation to Improve") +
  guides(fill=guide_legend(title="Noncompliance Incident / 'Strike'")) +
  theme(legend.position="bottom") +
  theme(axis.text.x=element_text(angle=15, vjust=.8, hjust=0.8))

modMotiv <- lmer(motivated ~ conditionSES * strike + ladder_Self + income_Self + ed_Own + study + conditionRace + (1|ResponseId), data=data, na.action=na.omit)

kable(anova(modMotiv))
```
:::

::: {.callout-note collapse="true"}
## First Impression of Patient Pain Severity

```{r}
#| warning: false
#| code-fold: true
ggplot(data=data, aes(conditionSES, severe)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  facet_wrap(~study) +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  theme_perez() +
  scale_fill_grey() +
  xlab("Condition") +
  ylab("Initial Perceived Pain Severity") +
  theme(legend.position="bottom")

modSevere <- lm(severe ~ conditionSES + study + income_Self + ladder_Self + ed_Own + study + conditionRace, data=data_wide)

kable(anova(modSevere))
```
:::

::: {.callout-note collapse="true"}
## Important to Me that Patient Health Improves

```{r, echo=F, warning=F, message=F}
#| warning: false
#| code-fold: true
modImport <- lmer(healthImproves ~ conditionSES * strike + ladder_Self + income_Self + ed_Own + study + conditionRace + (1|ResponseId), data=data, na.action=na.omit)

kable(anova(modImport))
```
:::

::: {.callout-note collapse="true"}
## I Should Have Been Clearer

```{r, echo=F, warning=F, message=F}
#| warning: false
#| code-fold: true
modClear <- lmer(clearer ~ conditionSES * strike + ladder_Self + income_Self + ed_Own + conditionRace + (1|ResponseId), data=data, na.action=na.omit)

kable(anova(modClear))
```
:::

::: {.callout-note collapse="true"}
## Attributions for Patient's Noncompliant Behavior

```{r, echo=F, warning=F, message=F}
#| warning: false
#| code-fold: true
ggplot(data=data, aes(conditionSES, attributions, fill=as.factor(strike))) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5), labels=c('100%\nInternal', 'More Internal\nthan External', 'Neither', 'More External\nthan Internal', '100%\nExternal')) +
  theme_perez() +
  scale_fill_grey() +
  xlab("Condition") +
  ylab("Attributions for Behavior") +
  guides(fill=guide_legend(title="Noncompliance Incident / 'Strike'")) +
  theme(legend.position="bottom") +
  theme(axis.text.x=element_text(angle=15, vjust=.8, hjust=0.8))

modAttrib <- lmer(attributions ~ conditionSES * strike + ladder_Self + race_Self + income_Self + study + conditionRace + (1|ResponseId), data=data)

kable(anova(modAttrib))
```
:::

::: {.callout-note collapse="true"}
## Perceived Likelihood of Patient Health Insurance

```{r, echo=F, warning=F, message=F}
#| warning: false
#| code-fold: true
ggplot(data=data, aes(conditionSES, insurance_Patient)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5), labels=c("1-Very\nLikely","2-Somewhat\nLikely","3-Neither","4-Somewhat\nUnlikely","5-Extremely\nUnlikely")) +
  theme_perez() +
  scale_fill_grey() +
  xlab("Patient") +
  ylab("Perceived Likelihood of Health Insurance") +
  guides(fill=guide_legend(title="Noncompliance Incident / 'Strike'")) +
  theme(legend.position="bottom") +
  theme(axis.text.x=element_text(angle=15, vjust=.8, hjust=0.8))

kable(anova(lm(insurance_Patient ~ conditionSES + ladder_Self + race_Self + income_Self + ed_Own + study + conditionRace, data_wide)))
```
:::

::: {.callout-note collapse="true"}
## Perceived Patient Health Literacy

```{r, echo=F, warning=F, message=F}
#| warning: false
#| code-fold: true
data %>% 
  filter(!is.na(patient)) %>% 
ggplot(aes(patient, healthLit_Patient)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  theme_perez() +
  scale_fill_grey() +
  xlab("Patient") +
  ylab("Perceived Health Literacy") +
  guides(fill=guide_legend(title="Noncompliance Incident / 'Strike'")) +
  theme(legend.position="bottom") +
  theme(axis.text.x=element_text(angle=15, vjust=.8, hjust=0.8))

kable(anova(lm(healthLit_Patient ~ conditionSES + conditionRace + ladder_Self + race_Self + income_Self + ed_Own + study, data_wide)))
```
:::