---
title: "01-Analyses_Study1"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

# Description

# Set-up

```{r libraries}
#| warning: false
#| message: false
#| code-fold: true
library(psych)
library(ggplot2)
library(effsize)
library(dplyr)
#library(kableExtra)
library(GPArotation)
library(stats)
library(plyr)
library(psych)
library(tidyverse)
library("Hmisc")
library(forcats)
library(grid)
library(ggcorrplot)
library(corrplot)
library(gridExtra)
library("ggdark")
library(broom)
library("effects")
library(lsmeans)
library(diagram)
library(pwr)
library(dplyr)
library(tidyr)
library(nlme)
library(rstatix)
library(multcomp)
library(lme4)
library(lmerTest)
library(knitr)
library(magrittr)
library(sjPlot)
library(ggpubr)
```

```{r ggplot-settings}
#| warning: false
#| message: false
#| code-fold: true
horzi_theme <- theme(    #   remove the gray background
  panel.background    = element_rect( size=.1, colour="black", fill="white") ,
  #   make the major gridlines light gray and thin
  panel.grid.major.y  = element_line( size=.1, colour="#666666" ) ,
  #   suppress the vertical grid lines
  panel.grid.major.x  = element_blank() ,
  #   suppress the minor grid lines
  panel.grid.minor    = element_blank() ,
  #   add axes
  axis.line           = element_line( size=.2 , colour="#666666" ),
  #   adjust the axis ticks
  axis.ticks          = element_line( size=.1 , colour="#666666" ),
  #   move the y-axis over to the left
  #axis.title.y        = element_text( angle=90, vjust=.5, hjust=.5 ),
  #   increase margin moved-over y-axis label fits
  # plot.margin = unit( c(.5,.25,.25,.5) , "in") ,
  title = element_text(  size=12 ) ,
  axis.title.x = element_text( size=12 ) ,
  axis.title.y = element_text( size=12 ) ,
  axis.text.x = element_text( size=12 ) ,
  axis.text.y = element_text( size=12 )
)

horzi <- horzi_theme

stat_sum_df <- function(fun, geom="crossbar", ...) {
  stat_summary(fun.data=fun, colour="black", geom=geom, width=.5,  ...)
}

# define the dodge object for equivalent error bar and geom_bar
dodge <- position_dodge(width=0.9)

# define a geom_bar
bars <- geom_bar(stat="summary", fun.y="mean", position="dodge")

theme_perez <- function() {
    ggplot2::theme_bw() +
    ggplot2::theme(
      axis.text = element_text(colour = "black",  family = "Times New Roman", size = 12),
    axis.title = element_text(colour = "black", family = "Times New Roman", size = 13),
    legend.title = element_text(colour = "black", family = "Times New Roman", size = 13),
    legend.text = element_text(colour = "black", family = "Times New Roman", size = 12),
    plot.title = element_text(colour = "black", family = "Times New Roman", size = 13),
    plot.subtitle = element_text(colour = "black", family = "Times New Roman", size = 13),
    strip.text = element_text(colour = "black", family = "Times New Roman", size = 13))
}
```

```{r data}
#| warning: false
#| message: false
#| code-fold: true
data <- read.csv("Data-Clean_Wide_20250212.csv")
dataLong <- read.csv("Data-Clean_Long_20250212.csv")
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
kable(table(data$Condition), col.names = list("Condition", "n"))
```

# Relationship Attitudes

::: {.panel-tabset}

#### α
```{r}
#| warning: false
#| message: false
#| code-fold: true
alpha_result <- psych::alpha(data[, c("manipCheck2", "manipCheck1")], check.keys=TRUE)
kable(alpha_result$total)
```

#### Plots
```{r}
#| warning: false
#| message: false
#| code-fold: true
item1 <- data %>% 
ggplot(aes(x=Condition, y=manipCheck1)) +
  geom_bar(stat="summary", position="dodge", fill = "grey40") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  geom_jitter(alpha = 0.3) +
  expand_limits(y = c(1, 6)) +
  theme_bw() +
  theme_perez() +
  labs(y = "It is NOT possible to prioritize a \nhigh-quality relationship with every patient.")

item2 <- data %>% 
ggplot(aes(x=Condition, y=manipCheck2)) +
  geom_bar(stat="summary", position="dodge", fill = "grey40") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  geom_jitter(alpha = 0.3) +
  expand_limits(y = c(1, 6)) +
  theme_bw() +
  theme_perez() +
  labs(y = "Patients will take advantage of you if \nyou ask for their input too often.")

plot <- ggarrange(item1, item2)

annotate_figure(plot, top = text_grob("Relationship Attitudes", face = "bold", size = 14))
```

#### Descriptives
```{r}
#| warning: false
#| message: false
#| code-fold: true
kable(psych::describe(data$manipCheck1), row.names = F, caption = "Item 1")

kable(psych::describe(data$manipCheck2), row.names = F, caption = "Item 2")
```

#### Models
```{r}
#| warning: false
#| message: false
#| code-fold: true
modManip1 <- lm(manipCheck1 ~ Condition + ladder + income + workInsurancePercent_1 + yearsWork_1 + trainingWhere + screener2, data)
tab_model(summary(modManip1), title = "It is NOT possible to prioritize a \nhigh-quality relationship with every patient.", show.se = T)

modManip2 <- lm(manipCheck2 ~ Condition + ladder + income + workInsurancePercent_1 + yearsWork_1 + trainingWhere + screener2, data)
tab_model(summary(modManip2), title = "Patients will take advantage of you if \nyou ask for their input too often.", show.se = T)
```

:::

# Vignette
## First Impression

::: {.panel-tabset}

#### Pain Severity
```{r}
#| warning: false
#| message: false
#| code-fold: true
tab_model(summary(lm(severe ~ Condition + insurance_Patient + ladder + income + workInsurancePercent_1 + yearsWork_1 + trainingWhere + screener2, data = data)))

kable(data %>% 
  filter(!is.na(severe)) %>% 
  dplyr::group_by(Condition) %>% 
  dplyr::summarise(mean = mean(severe)))
```

#### Pain Treatment 
```{r}
#| warning: false
#| message: false
#| code-fold: true
tab_model(summary(lm(treatmentDose_1_1 ~ Condition + insurance_Patient + ladder + income + workInsurancePercent_1 + yearsWork_1 + trainingWhere + screener2, data = data)))

kable(data %>% 
  filter(!is.na(treatmentDose_1_1)) %>% 
  dplyr::group_by(Condition) %>% 
  dplyr::summarise(mean = mean(treatmentDose_1_1)))
```

:::

## Outcomes

::: {.panel-tabset}

#### Patient Laziness
```{r}
#| warning: false
#| message: false
#| code-fold: true
kable(dataLong %>% 
        dplyr::group_by(Condition, strike) %>% 
        dplyr::summarise(mean(lazy),
                         sd(lazy)))

modLazy <- lmer(lazy ~ Condition * strike + insurance_Patient + ladder + income + workInsurancePercent_1 + yearsWork_1 + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

modLazy <- lmer(lazy ~ Condition + strike + insurance_Patient + ladder + income + workInsurancePercent_1 + yearsWork_1 + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

kable(anova(modLazy), caption = "Main Effect Model Output")

kable(emmeans(modLazy, pairwise ~ Condition * strike)$contrasts, caption = "Contrasts")

effectsize::eta_squared(modLazy, partial=T) %>% 
  kable(caption = "Effect Sizes")

ggplot(data=dataLong, aes(as.factor(strike), lazy, fill=Condition)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_bw() +
  theme_perez() +
  xlab("Noncompliance Incident / 'Strike'") +
  ylab("Patient Laziness") +
  guides(fill=guide_legend(title="Intervention Condition")) +
  theme(legend.position="bottom") 

kable(psych::describe(dataLong$lazy), row.names = F)
```

#### Patient Honesty
```{r}
#| warning: false
#| message: false
#| code-fold: true
modHon <- lmer(honest ~ Condition * strike + insurance_Patient + ladder + income + workInsurancePercent_1 + yearsWork_1 + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

modHon <- lmer(honest ~ Condition + insurance_Patient + strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

kable(anova(modHon), caption = "Main Effect Model Output")

kable(emmeans(modHon, pairwise ~ Condition * strike)$contrasts, caption = "Contrasts")

effectsize::eta_squared(modHon, partial=T) %>% 
  kable(caption = "Effect Sizes")

dataLong %>% 
  filter(!is.na(honest)) %>% 
  dplyr::group_by(Condition, strike) %>% 
  dplyr::summarise(mean(honest),
                   sd(honest))

ggplot(data=dataLong, aes(as.factor(strike), honest, fill=Condition)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_bw() +
  theme_perez() +
  xlab("Noncompliance Incident / 'Strike'") +
  ylab("Patient Honesty") +
  guides(fill=guide_legend(title="Intervention Condition")) +
  theme(legend.position="bottom") 

kable(psych::describe(dataLong$honest), row.names = F)
```

#### Patient Pain Exaggeration
```{r}
#| warning: false
#| message: false
#| code-fold: true
modExag <- lmer(exaggerate ~ Condition * strike + insurance_Patient  + ladder + income + workInsurancePercent_1 + yearsWork_1 + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

modExag <- lmer(exaggerate ~ Condition + insurance_Patient + strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

kable(anova(modExag), caption = "Main Effect Model Output")

kable(emmeans(modExag, pairwise ~ Condition * strike)$contrasts, caption = "Contrasts")

effectsize::eta_squared(modExag, partial=T) %>% 
  kable(caption = "Effect Sizes")

dataLong %>% 
  filter(!is.na(exaggerate)) %>% 
  dplyr::group_by(Condition) %>% 
  dplyr::summarise(mean(exaggerate),
                   sd(exaggerate))

ggplot(data=dataLong, aes(as.factor(Condition), exaggerate)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_minimal() +
  xlab("Intervention Condition") +
  ylab("Patient Exaggerating Pain") +
  guides(fill=guide_legend(title="Intervention Condition")) +
  theme(legend.position="bottom")

kable(psych::describe(dataLong$exaggerate), row.names = F)
```

## Equity Engagement 
```{r}
#| warning: false
#| message: false
#| code-fold: true
data <- data %>% 
  mutate(sdoh1_z = scale(sdoh1),
         sdoh2_z = scale(sdoh2), 
         culturalCompetancy1_z = scale(culturalCompetancy1),
         culturalCompetancy2_z = scale(culturalCompetancy2),
         petition1_z = scale(petition1),
         petition2_z = scale(petition2),
         donation_1_z = scale(donation_1))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
alpha_result <- psych::alpha(data[, c("sdoh1_z", "sdoh2_z", "culturalCompetancy1_z", "culturalCompetancy2_z", "petition1_z", "petition2_z", "donation_1_z")], check.keys=TRUE)

kable(alpha_result$total, row.names = F)

data$equity_beh <- scoreItems(keys = c(1, 1, 1, 1, 1, 1, 1),
                               items = data[, c("sdoh1_z", "sdoh2_z", "culturalCompetancy1_z", "culturalCompetancy2_z", "petition1_z", "petition2_z", "donation_1_z")])$scores
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
tab_model(lm(equity_beh ~ Condition + yearsWork_1 + workInsurancePercent_1 + trainingWhere + screener2, data = data))

ggplot(data=data, aes(as.factor(Condition), equity_beh)) +
  geom_boxplot() +
  scale_fill_grey() +
  theme_minimal() +
  xlab("Intervention Condition") +
  ylab("Equity Behavioral Intentions") +
  theme(legend.position="bottom") 

kable(data %>% 
        dplyr::group_by(Condition) %>% 
        dplyr::summarise(mean = mean(equity_beh),
                         sd = sd(equity_beh)))

kable(psych::describe(data$equity_beh), row.names = F)
```


#### Treatment Decisions 
```{r}
#| warning: false
#| message: false
#| code-fold: true
modTreat <- lmer(treatAvg ~ Condition * strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

modTreat <- lmer(treatAvg ~ Condition + strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

kable(anova(modTreat), title = "Main Effect Model Output")

kable(emmeans(modTreat, pairwise ~ Condition * strike)$contrasts, caption = "Contrasts")

effectsize::eta_squared(modTreat, partial=T) %>% 
  kable(caption = "Effect Sizes")

dataLong %>% 
  filter(!is.na(treatAvg)) %>% 
  dplyr::group_by(strike) %>% 
  dplyr::summarise(mean(treatAvg),
                   sd(treatAvg))

ggplot(data=dataLong, aes(as.factor(Condition), treatAvg)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:4)) +
  scale_y_continuous(breaks=c(1:4)) +
  scale_fill_grey() +
  theme_bw() +
  theme_perez() +
  xlab("Intervention Condition") +
  ylab("Treatment Decisions") +
  theme(legend.position="bottom")

kable(psych::describe(dataLong$treatAvg), row.names = F)
```

:::

## Additional Outcomes 

::: {.panel-tabset}

#### Frustration
```{r}
#| warning: false
#| message: false
#| code-fold: true
modFrust <- lmer(frustrating ~ Condition * strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 +  (1|ResponseId), data=dataLong, na.action=na.omit)

modFrust <- lmer(frustrating ~ Condition + strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 +  (1|ResponseId), data=dataLong, na.action=na.omit)

kable(anova(modFrust), title = "Main Effect Model Output")

dataLong %>% 
  filter(!is.na(frustrating)) %>% 
  dplyr::group_by(Condition) %>% 
  dplyr::summarise(mean = mean(frustrating))

ggplot(data=dataLong, aes(as.factor(strike), frustrating, fill=Condition)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_minimal() +
  xlab("Noncompliance Incident / 'Strike'") +
  ylab("Patient Frustrating") +
  guides(fill=guide_legend(title="Intervention Condition")) +
  theme(legend.position="bottom") 
```

#### Desire to Give Up
```{r}
#| warning: false
#| message: false
#| code-fold: true
modGiveUp <- lmer(givingUp ~ Condition * strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

modGiveUp <- lmer(givingUp ~ Condition + strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

kable(anova(modGiveUp), title = "Main Effect Model Output")

dataLong %>% 
  filter(!is.na(givingUp)) %>% 
  dplyr::group_by(Condition) %>% 
  dplyr::summarise(mean = mean(givingUp))

ggplot(data=dataLong, aes(as.factor(strike), givingUp, fill=Condition)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_minimal() +
  xlab("Noncompliance Incident / 'Strike'") +
  ylab("Giving Up") +
  guides(fill=guide_legend(title="Intervention Condition")) +
  theme(legend.position="bottom") 

kable(psych::describe(dataLong$givingUp), row.names = F)
```

#### Patient Deservingness
```{r}
#| warning: false
#| message: false
#| code-fold: true
modDeserve <- lmer(deserve ~ Condition * strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

modDeserve <- lmer(deserve ~ Condition + strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

kable(anova(modDeserve), title = "Main Effect Model Output")

ggplot(data=dataLong, aes(as.factor(strike), deserve, fill=Condition)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_minimal() +
  xlab("Noncompliance Incident / 'Strike'") +
  ylab("Deserves Help") +
  guides(fill=guide_legend(title="Intervention Condition")) +
  theme(legend.position="bottom") 
```

#### Patient Motivation
```{r}
#| warning: false
#| message: false
#| code-fold: true
modMotiv <- lmer(motivated ~ Condition * strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

modMotiv <- lmer(motivated ~ Condition + strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

kable(anova(modMotiv), title = "Main Effect Model Output")

ggplot(data=dataLong, aes(as.factor(strike), motivated, fill=Condition)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_minimal() +
  xlab("Noncompliance Incident / 'Strike'") +
  ylab("Patient Motivated") +
  guides(fill=guide_legend(title="Intervention Condition")) +
  theme(legend.position="bottom") 
```

#### Patient Intelligence
```{r}
#| warning: false
#| message: false
#| code-fold: true
modIntell <- lmer(intelligent ~ Condition * strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

modIntell <- lmer(intelligent ~ Condition + strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

kable(anova(modIntell), title = "Main Effect Model Output")

ggplot(data=dataLong, aes(as.factor(strike), intelligent, fill=Condition)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_minimal() +
  xlab("Noncompliance Incident / 'Strike'") +
  ylab("Patient Intelligence") +
  guides(fill=guide_legend(title="Intervention Condition")) +
  theme(legend.position="bottom") 
```

#### Attributions for Noncompliance
```{r}
#| warning: false
#| message: false
#| code-fold: true
modAttrib <- lmer(attributions ~ Condition * strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

modAttrib <- lmer(attributions ~ Condition + strike + ladder + income + workInsurancePercent_1 + yearsWork_1 + insurance_Patient + trainingWhere + screener2 + (1|ResponseId), data=dataLong, na.action=na.omit)

kable(anova(modAttrib), title = "Main Effect Model Output")

ggplot(data=dataLong, aes(as.factor(strike), attributions, fill=Condition)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_minimal() +
  xlab("Noncompliance Incident / 'Strike'") +
  ylab("Attributons for Patient Behavior") +
  guides(fill=guide_legend(title="Intervention Condition")) +
  theme(legend.position="bottom") 
```

:::

# Perceived Patient SES

::: {.panel-tabset}

#### Ladder (Subjective SES)
```{r}
#| warning: false
#| message: false
#| code-fold: true
hist(data$ladder_Patient, xlab = "Ladder Position", main = "")
kable(psych::describe(data$ladder_Patient), row.names = F)
```

#### Income
```{r}
#| warning: false
#| message: false
#| code-fold: true
kable(table(factor(data$income_Patient, labels = c("<$15k", "$15-30k", "$31-50k", "$50-75k", "$75-100k", "$100-150k", "$150k+"))), col.names = c("Income", "n"))
kable(psych::describe(data$income_Patient), row.names = F)
```

#### Education
```{r}
#| warning: false
#| message: false
#| code-fold: true
kable(table(factor(data$ed_Patient, labels = c("< HS", "HS", "College", "Postgrad"))), col.names = c("Education Level", "n"))
```

#### Health Insurance
```{r}
#| warning: false
#| message: false
#| code-fold: true
hist(data$insurance_Patient, xlab = "Likelihood of Health Insurance", main = "")

kable(psych::describe(data$insurance_Patient), row.names = F)
```

:::

# Additional DVs

## Trainings 

```{r}
alpha_result <- psych::alpha(data[, c("sdoh1", "sdoh2", "culturalCompetancy1", "culturalCompetancy2")], check.keys=TRUE)

kable(alpha_result$total, row.names = F)

keys.list <- list(c("sdoh1", "sdoh2", "culturalCompetancy1", "culturalCompetancy2"))

data$trainings <- scoreItems(keys = c(1, 1, 1, 1),
                               items = data[, c("sdoh1", "sdoh2", "culturalCompetancy1", "culturalCompetancy2")],
                               min = 1, 
                               max = 5)$scores

tab_model(lm(trainings ~ Condition + yearsWork_1 + workInsurancePercent_1 + trainingWhere + screener2, data = data))

ggplot(data=data, aes(as.factor(Condition), trainings)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_minimal() +
  xlab("Intervention Condition") +
  ylab("Behavioral Intentions") +
  theme(legend.position="bottom") 

kable(psych::describe(data$trainings), row.means = F)
```

:::

## Petitions
```{r}
alpha_result <- psych::alpha(data[, c("petition1", "petition2")], check.keys=TRUE)
kable(alpha_result$total, row.names = F)

keys.list <- list(c("petition1", "petition2"))

data$petitions <- scoreItems(keys = c(1, 1),
                               items = data[, c("petition1", "petition2")],
                               min = 0, 
                               max = 1)$scores

summary(glm(petitions ~ Condition + workInsurancePercent_1 + trainingWhere + screener2, data = data, family = binomial))

kable(table(data$petitions))

# table(factor(data$petition1))
# table(factor(data$petition2))
```

## Donation
```{r}
#| warning: false
#| message: false
#| code-fold: true
kable(psych::describe(data$donation_1))

summary(lm(donation_1 ~ Condition + workInsurancePercent_1 + trainingWhere + screener2, data))
summary(lm(donation_2 ~ Condition + workInsurancePercent_1 + trainingWhere + screener2, data))
```

## Anticipated Professional Fulfillment Index

::: {.panel-tabset}

#### Overall
```{r} 
alpha_result <- psych::alpha(data[, c("PFI1_1", "PFI1_2", "PFI1_3", "PFI1_4", "PFI1_5", "PFI1_6", "PFI2_1", "PFI2_2", "PFI2_3", "PFI2_4", "PFI3_1", "PFI3_2", "PFI3_3", "PFI3_4", "PFI3_5", "PFI3_6")], check.keys=TRUE)

kable(alpha_result$total, row.names = F) # Overall alpha
# print(alpha_result$alpha.drop) # Alpha if item deleted
# print(alpha_result$item.stats) # Item statistics

data %<>% mutate(PFI = ((PFI1_1 + PFI1_2 + PFI1_3 + PFI1_4 + PFI1_5 + PFI1_6 + PFI2_1 + PFI2_2 + PFI2_3 + PFI2_4 + PFI3_1 + PFI3_2 + PFI3_3 + PFI3_4 + PFI3_5 + PFI3_6) / 16))

tab_model(lm(PFI ~ Condition + yearsWork_1, data = data), title = "PFI - Overall")
kable(psych::describe(data$PFI), row.names = F)
```

#### Professional Fulfillment
```{r} 
alpha_result <- psych::alpha(data[, c("PFI1_1", "PFI1_2", "PFI1_3", "PFI1_4", "PFI1_5", "PFI1_6")])

kable(alpha_result$total, row.names = F) # Overall alpha
# print(alpha_result$alpha.drop) # Alpha if item deleted
# print(alpha_result$item.stats) # Item statistics

data %<>% mutate(PFI_PF = ((PFI1_1 + PFI1_2 + PFI1_3 + PFI1_4 + PFI1_5 + PFI1_6) / 6))

tab_model(lm(PFI_PF ~ Condition + yearsWork_1, data = data), title = "PFI - Professional Fulfillment")
kable(psych::describe(data$PFI_PF), row.names = F)
```

#### Work Exhaustion
```{r burnout} 
alpha_result <- psych::alpha(data[, c("PFI2_1", "PFI2_2", "PFI2_3", "PFI2_4")])

kable(alpha_result$total, row.names = F) # Overall alpha
# print(alpha_result$alpha.drop) # Alpha if item deleted
# print(alpha_result$item.stats) # Item statistics

data %<>% mutate(PFI_exhaustion = ((PFI2_1 + PFI2_2 + PFI2_3 + PFI2_4) / 4))

tab_model(lm(PFI_exhaustion ~ Condition + yearsWork_1, data = data), title = "PFI - Work Exhaustion")
kable(psych::describe(data$PFI_exhaustion), row.names = F)
```

#### Interpersonal Disengagement
```{r}
alpha_result <- psych::alpha(data[, c("PFI3_1", "PFI3_2", "PFI3_3", "PFI3_4", "PFI3_5", "PFI3_6")])

kable(alpha_result$total, row.names = F) # Overall alpha
# print(alpha_result$alpha.drop) # Alpha if item deleted
# print(alpha_result$item.stats) # Item statistics

data %<>% mutate(PFI_disengagement = ((PFI3_1 + PFI3_2 + PFI3_3 + PFI3_4 + PFI3_5 + PFI3_6) / 6))

tab_model(lm(PFI_disengagement ~ Condition + yearsWork_1, data = data), title = "PFI - Disengagement")
kable(psych::describe(data$PFI_disengagement), row.names = F)
```

:::

# Demographics

#### Personal
```{r}
# RACE
kable(data %>% 
  mutate(race = factor(race, labels = c("White", "Asian", "Black", "Latinx", "East Asian", "Multiracial", "Other"))) %>% 
  group_by(race) %>%
  tally(name = "total") %>% 
  mutate(percentage = total / sum(total) * 100))

# GENDER
kable(data %>% 
  mutate(gender = factor(gender, labels = c("Male", "Female"))) %>% 
  group_by(gender) %>%
  tally(name = "total") %>% 
  mutate(percentage = total / sum(total) * 100))

# POLITICS
psych::describe(data$politics)

# EDUCATION
kable(data %>% 
  mutate(edOwn = factor(edOwn, labels = c("HS", "College", "Postgrad"))) %>% 
  group_by(edOwn) %>%
  tally(name = "total") %>% 
  mutate(percentage = total / sum(total) * 100))

# INCOME
kable(data %>% 
  mutate(income = factor(income, labels = c("<15k", "15-30", "30-50", "50-75", "75-100", "100-150", "150+"))) %>% 
  group_by(income) %>% 
    tally(name = "total") %>% 
    mutate(percentage = total / sum(total) * 100))

hist(data$income)
psych::describe(data$income)

# LADDER
hist(data$ladder)
psych::describe(data$ladder)
```

#### Work
```{r}
hist(data$yearsWork_1)
psych::describe(data$yearsWork_1)

table(factor(data$trainingWhere, labels = c("USA", "Not USA")))

hist(data$workInsurancePercent)
psych::describe(data$workInsurancePercent)

kable(data %>% 
  mutate(screener2 = factor(screener2, labels = c("Doctor", "RN", "PA", "NP"))) %>% 
  group_by(screener2) %>%
  tally(name = "total") %>% 
  mutate(percentage = total / sum(total) * 100))
```

