---
title: "Healthcare Intervention Analyses - Pilot"
author: "Sierra Semko"
output:
  html_document:
    toc: true
    toc_depth: 3
editor_options:
  chunk_output_type: console
---

# Set-up

```{r packages}
#| warning: false
#| message: false
#| include: false
library(psych)
library(ggplot2)
library(effsize)
library(dplyr)
# library(kableExtra)
library(GPArotation)
library(stats)
library(plyr)
library(psych)
library(tidyverse)
library("Hmisc")
library(forcats)
library(grid)
library(ggcorrplot)
library(corrplot)
library(gridExtra)
library("ggdark")
library(broom)
library("effects")
library(lsmeans)
library(diagram)
library(pwr)
library(dplyr)
library(tidyr)
library(nlme)
library(rstatix)
library(multcomp)
library(lme4)
library(lmerTest)
library(readxl)
library(knitr)
library(sjPlot)
```

```{r ggplot}
#| warning: false
#| message: false
#| include: false
horzi_theme <- theme(    #   remove the gray background
  panel.background    = element_rect( size=.1, colour="black", fill="white") ,
  #   make the major gridlines light gray and thin
  panel.grid.major.y  = element_line( size=.1, colour="#666666" ) ,
  #   suppress the vertical grid lines
  panel.grid.major.x  = element_blank() ,
  #   suppress the minor grid lines
  panel.grid.minor    = element_blank() ,
  #   add axes
  axis.line           = element_line( size=.2 , colour="#666666" ),
  #   adjust the axis ticks
  axis.ticks          = element_line( size=.1 , colour="#666666" ),
  #   move the y-axis over to the left
  #axis.title.y        = element_text( angle=90, vjust=.5, hjust=.5 ),
  #   increase margin moved-over y-axis label fits
  # plot.margin = unit( c(.5,.25,.25,.5) , "in") ,
  title = element_text(  size=12 ) ,
  axis.title.x = element_text( size=12 ) ,
  axis.title.y = element_text( size=12 ) ,
  axis.text.x = element_text( size=12 ) ,
  axis.text.y = element_text( size=12 )
)

horzi <- horzi_theme

stat_sum_df <- function(fun, geom="crossbar", ...) {
  stat_summary(fun.data=fun, colour="black", geom=geom, width=.5,  ...)
}

# define the dodge object for equivalent error bar and geom_bar
dodge <- position_dodge(width=0.9)

# define a geom_bar
bars <- geom_bar(stat="summary", fun.y="mean", position="dodge")
```

```{r data}
#| warning: false
#| message: false
#| echo: false
#| code-fold: true
data <- read_excel("Healthcare-Intervention-Relevant-Roles.xlsx")

data <- data[-1,]

data$condition <- case_when(data$Condition == "1" ~ "Treatment",
                            data$Condition == "0" ~ "Control", 
                            TRUE ~ "NA")
```

# Data Cleaning
## Removing Unassigned Participants
```{r}
#| warning: false
#| message: false
#| code-fold: true
data <- data %>% 
  filter(condition != "NA")
```

1 participant was not assigned and was removed. 

## Response Time
```{r}
#| warning: false
#| message: false
#| code-fold: true
data$`Duration (in seconds)` <- as.numeric(data$`Duration (in seconds)`)
hist(data$`Duration (in seconds)`)
summary(data$`Duration (in seconds)`)
IQR(data$`Duration (in seconds)`)

outliers <- 1.5*2421

lower <- 1397-outliers
upper <- 2498+outliers

outliers <- data %>% 
  filter(`Duration (in seconds)` < lower | `Duration (in seconds)` > upper)

remove <- outliers$ResponseId

`%!in%` <- Negate(`%in%`)

data <- data %>% 
  filter(ResponseId %!in% remove)
```

3 participants removed. 

# Demographics

::: {.panel-tabset}

#### Gender
```{r}
#| warning: false
#| message: false
#| code-fold: true
kable(prop.table(table(data$gender)), col.names = c("Gender", "n"))
```

#### Race
```{r}
#| warning: false
#| message: false
#| code-fold: true
kable(prop.table(table(data$race)), col.names = c("Race", "n"))
```

#### Number of Years Worked in Profession
```{r}
#| warning: false
#| message: false
#| code-fold: true
ggplot(data, aes(x=as.numeric(yearsWork_1))) +
  geom_histogram(fill='#deebf7', color='#3182bd') +
  theme_minimal() +
  geom_vline(xintercept = 4, colour="red", linetype="longdash")

kable(psych::describe(as.numeric(data$yearsWork_1), na.rm=TRUE), row.names = F)
```

**<span style="color: #3182bd;">Median number of years in profession</span>**

#### Exposure to Low-SES Patients
```{r}
#| warning: false
#| message: false
#| code-fold: true
kable(psych::describe(as.numeric(data$insurance_1), na.rm=TRUE), row.names = F)
```

#### Level of Education
```{r}
#| warning: false
#| message: false
#| code-fold: true
data$edOwn <- as.factor(data$edOwn)
levels(data$edOwn) <- c("High School", "College", "Postgraduate")
kable(prop.table(table(data$edOwn)), col.names = c("Education", "n"))
```

#### Ladder
```{r}
#| warning: false
#| message: false
#| code-fold: true
ggplot(data, aes(x=as.numeric(ladder))) +
  geom_density(fill='#deebf7', color='#3182bd') +
  theme_minimal() +
  geom_vline(xintercept = 6, colour="red", linetype="longdash")

kable(psych::describe(as.numeric(data$ladder), na.rm=TRUE), row.names = F)
```

**<span style="color: #3182bd;">Median position on MacArthur Ladder (1 - lowest rung; 10 - highest rung)</span>**

#### Household Income
```{r}
#| warning: false
#| message: false
#| code-fold: true
ggplot(data, aes(x=as.numeric(income))) +
  geom_density(fill='#deebf7', color='#3182bd') +
  theme_minimal() +
  geom_vline(xintercept = 5, colour="red", linetype="longdash")

kable(psych::describe(as.numeric(data$income), na.rm=TRUE), row.names = F)
```

**<span style="color: #3182bd;">Median income is between $75,001 and $100,000</span>**

#### Politics
```{r}
#| warning: false
#| message: false
#| code-fold: true
ggplot(data, aes(x=as.numeric(politics))) +
  geom_density(fill='#deebf7', color='#3182bd') +
  theme_minimal()

kable(psych::describe(as.numeric(data$politics)), row.names = F)
```

**<span style="color: #3182bd;">1 = Extremely Liberal, 7 = Extremely Conservative</span>**

:::

# Outcomes 
## Relationship Attitudes
```{r}
#| warning: false
#| message: false
#| code-fold: true
tab_model(lm(manipulationCheck ~ condition + as.numeric(yearsWork_1), data))

kable(psych::describe(as.numeric(data$manipulationCheck)), row.names = F)

kable(data %>% 
      dplyr::group_by(condition) %>% 
      dplyr::summarise(mean = mean(as.numeric(manipulationCheck)),
                       sd = sd(as.numeric(manipulationCheck))))

ggplot(data, aes(x=condition, y=as.numeric(manipulationCheck))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_bw() +
  xlab("Intervention Condition") +
  ylab("Relationship Attitudes") +
  theme(legend.position="bottom") 
```

## Scenario

*<span style="color: #3182bd;">Consider the following patient: After a healthcare visit to address her diabetes, a patient describes how she does not think that doctors and nurses are fair to people like her. She explains that this belief makes her nervous about going to clinics or hospitals, and about following the treatment plans that her doctor devises.</span>* 

*<span style="color: #3182bd;">How would you respond to this patient? Please respond with at least three meaningful sentences to share.</span>*

### Patient is lazy
```{r}
#| warning: false
#| message: false
#| code-fold: true
tab_model(lm(lazy ~ condition + as.numeric(yearsWork_1), data))

kable(psych::describe(as.numeric(data$lazy)), row.names = F)

kable(data %>% 
      dplyr::group_by(condition) %>% 
      dplyr::summarise(mean = mean(as.numeric(lazy)),
                       sd = sd(as.numeric(lazy))))

ggplot(data, aes(x=condition, y=as.numeric(lazy))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5)) +
    stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_bw() +
  xlab("Intervention Condition") +
  ylab("Patient Laziness") +
  theme(legend.position="bottom") 
```

### I feel like giving up on patient 
```{r}
#| warning: false
#| message: false
#| code-fold: true
tab_model(lm(givingUp ~ condition + as.numeric(yearsWork_1), data))

kable(psych::describe(as.numeric(data$givingUp)), row.names = F)

kable(data %>% 
      dplyr::group_by(condition) %>% 
      dplyr::summarise(mean = mean(as.numeric(givingUp)),
                       sd = sd(as.numeric(givingUp))))

ggplot(data, aes(x=condition, y=as.numeric(givingUp))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5)) +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_bw() +
  xlab("Intervention Condition") +
  ylab("Desire to Give Up") +
  theme(legend.position="bottom") 
```

## Equity Engagement Index

```{r}
#| warning: false
#| message: false
#| code-fold: true
data <- data %>% 
  mutate(sdoh1 = as.numeric(sdoh1),
         sdoh2 = as.numeric(sdoh2), 
         culturalCompetancy1 = as.numeric(culturalCompetancy1),
         culturalCompetancy2 = as.numeric(culturalCompetancy2),
         petition1 = as.numeric(petition1),
         petition2 = as.numeric(petition2)) %>% 
  mutate(sdoh1_z = scale(sdoh1),
         sdoh2_z = scale(sdoh2), 
         culturalCompetancy1_z = scale(culturalCompetancy1),
         culturalCompetancy2_z = scale(culturalCompetancy2),
         petition1_z = scale(petition1),
         petition2_z = scale(petition2))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
alpha_result <- psych::alpha(data[, c("sdoh1_z", "sdoh2_z", "culturalCompetancy1_z", "culturalCompetancy2_z", "petition1_z", "petition2_z")], check.keys=TRUE)

kable(alpha_result$total, row.names = F)

data$equity_beh <- scoreItems(keys = c(1, 1, 1, 1, 1, 1),
                               items = data[, c("sdoh1_z", "sdoh2_z", "culturalCompetancy1_z", "culturalCompetancy2_z", "petition1_z", "petition2_z")])$scores
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
tab_model(lm(equity_beh ~ Condition + as.numeric(yearsWork_1), data))

kable(data %>% 
      dplyr::group_by(condition) %>% 
      dplyr::summarise(mean = mean(as.numeric(equity_beh)),
                       sd = sd(as.numeric(equity_beh))))

ggplot(data=data, aes(as.factor(Condition), equity_beh)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  scale_fill_grey() +
  theme_minimal() +
  xlab("Intervention Condition") +
  ylab("Equity Behavioral Intentions") +
  theme(legend.position="bottom") 
```

# Additional Analyses
## Comfort Answering Questions
```{r}
#| warning: false
#| message: false
#| code-fold: true
kable(table(data$comfort))
```

## Professional Fulfillment Index
```{r}
#| warning: false
#| message: false
#| code-fold: true
data <- data %>% 
  mutate_at(c("PFI1_1", "PFI1_2", "PFI1_3", "PFI1_4", "PFI1_5", "PFI1_6", "PFI2_1", "PFI2_2", "PFI2_3", "PFI2_4", "PFI3_1", "PFI3_2", "PFI3_3", "PFI3_4"), as.numeric)

keys.list <- list(PFI_fulfill = c('PFI1_1', 'PFI1_2', 'PFI1_3', 'PFI1_4', 'PFI1_5', 'PFI1_6'),
                  PFI_exhaust = c('PFI2_1', 'PFI2_2', 'PFI2_3', 'PFI2_4'),
                  PFI_disengage = c('PFI3_1', 'PFI3_2', 'PFI3_3', 'PFI3_4'))

scores <- scoreItems(keys.list, data, min = 1, max = 5)  
summary(scores, short = F)

data$PFI_fulfill = scoreItems(keys.list, data, min=1, max=5)$score[,1] 
data$PFI_exhaust = scoreItems(keys.list, data, min=1, max=5)$score[,2] 
data$PFI_disengage = scoreItems(keys.list, data, min=1, max=5)$score[,3] 
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
mod <- lm(PFI_fulfill ~ condition, data)
summary(mod)

ggplot(data, aes(x=condition, y=as.numeric(PFI_fulfill))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
mod <- lm(PFI_exhaust ~ condition, data)
summary(mod)

ggplot(data, aes(x=condition, y=as.numeric(PFI_exhaust))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
mod <- lm(PFI_disengage ~ condition, data)
summary(mod)

ggplot(data, aes(x=condition, y=as.numeric(PFI_disengage))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
PFI_fulfill_1 <- lm(lazy ~ PFI_fulfill * condition, data)
summary(PFI_fulfill_1)

PFI_fulfill_2 <- lm(givingUp ~ PFI_fulfill * condition, data)
summary(PFI_fulfill_2)

PFI_fulfill_3 <- lm(attributions ~ PFI_fulfill * condition, data)
summary(PFI_fulfill_3)

ggplot(data, aes(color = condition, y = as.numeric(givingUp), x = PFI_fulfill)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("Professional Fulfillment") +
  ylab("Desire to Give Up on Patient") +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
PFI_exhaust_1 <- lm(lazy~PFI_exhaust*condition, data)
summary(PFI_exhaust_1)

PFI_exhaust_2 <- lm(givingUp~PFI_exhaust*condition, data)
summary(PFI_exhaust_2)

PFI_exhaust_3 <- lm(attributions~PFI_exhaust*condition, data)
summary(PFI_exhaust_3)
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
PFI_disengage_1 <- lm(lazy~PFI_disengage*condition, data)
summary(PFI_disengage_1)

PFI_disengage_2 <- lm(givingUp~PFI_disengage*condition, data)
summary(PFI_disengage_2)

PFI_disengage_3 <- lm(attributions~PFI_disengage*condition, data)
summary(PFI_disengage_3)
```

## Workload
```{r}
#| warning: false
#| message: false
#| code-fold: true
data$nasatlxMental_1 <- as.numeric(data$nasatlxMental_1)
data$nasatlxTemporal_1 <- as.numeric(data$nasatlxTemporal_1)
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
mental_1 <- lm(lazy~nasatlxMental_1*condition, data)
summary(mental_1)

mental_2 <- lm(givingUp~nasatlxMental_1*condition, data)
summary(mental_2)

mental_3 <- lm(attributions~nasatlxMental_1*condition, data)
summary(mental_3)
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
cor(data$nasatlxMental_1, data$PFI_disengage)
cor(data$nasatlxMental_1, data$PFI_exhaust)
cor(data$nasatlxMental_1, data$PFI_fulfill)
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
temporal_1 <- lm(lazy~nasatlxTemporal_1*condition, data)
summary(temporal_1)

temporal_2 <- lm(givingUp~nasatlxTemporal_1*condition, data)
summary(temporal_2)

temporal_3 <- lm(attributions~nasatlxTemporal_1*condition, data)
summary(temporal_3)
```

## Social Determinants of Health

::: {.panel-tabset}

#### Learning More
```{r}
#| warning: false
#| message: false
#| code-fold: true
t.test(as.numeric(data$sdoh1) ~ data$condition)

ggplot(data, aes(x=condition, y=as.numeric(sdoh1))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

#### 10-hour Training
```{r}
#| warning: false
#| message: false
#| code-fold: true
t.test(as.numeric(data$sdoh2) ~ data$condition)

ggplot(data, aes(x=condition, y=as.numeric(sdoh2))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

:::

## Cultural Competency

::: {.panel-tabset}

### Learning More
```{r}
#| warning: false
#| message: false
#| code-fold: true
t.test(as.numeric(data$culturalCompetancy1) ~ data$condition)

ggplot(data, aes(x=condition, y=as.numeric(culturalCompetancy1))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

#### 10-hour Training
```{r}
#| warning: false
#| message: false
#| code-fold: true
t.test(as.numeric(data$culturalCompetancy2) ~ data$condition)

ggplot(data, aes(x=condition, y=as.numeric(culturalCompetancy2))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
alpha_result <- psych::alpha(data[, c("sdoh1", "sdoh2", "culturalCompetancy1", "culturalCompetancy2")], check.keys=TRUE)

kable(alpha_result$total, row.names = F)

keys.list <- list(c("sdoh1", "sdoh2", "culturalCompetancy1", "culturalCompetancy2"))

data$trainings <- scoreItems(keys = c(1, 1, 1, 1),
                               items = data[, c("sdoh1", "sdoh2", "culturalCompetancy1", "culturalCompetancy2")],
                               min = 1, 
                               max = 5)$scores

t.test(trainings ~ Condition, data)

ggplot(data=data, aes(as.factor(Condition), trainings)) +
  geom_bar(stat="summary", fun.y="mean", position="dodge") +
  stat_sum_df("mean_cl_boot", geom = "errorbar", position= position_dodge(.9), conf.int=.68, width=0.2) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  scale_fill_grey() +
  theme_minimal() +
  xlab("Intervention Condition") +
  ylab("Behavioral Intentions") +
  theme(legend.position="bottom") 
```

:::

## Petitions
```{r}
#| warning: false
#| message: false
#| code-fold: true
alpha_result <- psych::alpha(data[, c("petition1", "petition2")], check.keys=TRUE)
kable(alpha_result$total, row.names = F)

keys.list <- list(c("petition1", "petition2"))

data$petitions <- scoreItems(keys = c(1, 1),
                               items = data[, c("petition1", "petition2")],
                               min = 0, 
                               max = 1)$scores

summary(glm(petitions ~ condition, data = data, family = binomial))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
data$petition1 <- as.factor(data$petition1)

mod_log1 <- glm(petition1 ~ condition, data=data, family = binomial)
summary(mod_log1)

mod_log1 %>%
tidy(exponentiate = T, conf.int = T) %>%
mutate_if(is.numeric, ~ round(.,3))

prop.table(table(data$condition, data$petition1))

ggplot(data, aes(x=petition1, fill = condition)) +
  geom_bar(fun="mean", stat="count", position="dodge") +
  scale_x_discrete(labels = c("Do not add my name", "Add my name")) +
  theme_bw()

data$petition2 <- as.factor(data$petition2)

mod_log2 <- glm(formula = petition2 ~ condition, data=data, family = binomial)

mod_log2 %>%
tidy(exponentiate = T, conf.int = T) %>%
mutate_if(is.numeric, ~ round(.,3))

ggplot(data, aes(x=petition2, fill = condition)) +
  geom_bar(fun="mean", stat="count", position="dodge") +
  scale_x_discrete(labels = c("Do not add my name", "Add my name")) +
  theme_bw()

prop.table(table(data$condition, data$petition2))
```

## Donations
```{r}
#| warning: false
#| message: false
#| code-fold: true
data$donation_1 <- as.numeric(data$donation_1)
data$donation_2 <- as.numeric(data$donation_2)

t.test(data$donation_1 ~ data$condition)

ggplot(data, aes(x=condition, y=as.numeric(donation_1))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(0,100))

t.test(data$donation_2 ~ data$condition)

ggplot(data, aes(x=condition, y=as.numeric(donation_2))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(0,100))

data$donation_diff <- data$donation_1 - data$donation_2
t.test(data$donation_diff ~ data$condition)

ggplot(data, aes(x=condition, y=as.numeric(donation_diff))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(0,100))
```

## Scenario

::: {.panel-tabset}

#### Patient is lazy
```{r}
#| warning: false
#| message: false
#| code-fold: true
summary(lm(lazy ~ condition * IRI2, data))
summary(lm(lazy ~ condition * IRI4, data))
summary(lm(lazy ~ condition * IRI6, data))

ggplot(data, aes(color = condition, y = as.numeric(lazy), x = IRI4)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("If I'm sure I'm right about something, I don't \nwaste much time listening to patients’ arguments.") +
  ylab("Patient Laziness") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

ggplot(data, aes(color = condition, y = as.numeric(lazy), x = IRI6)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("When I'm frustrated with a patient, I usually try \nto put myself in his/her shoes for a while.") +
  ylab("Patient Laziness") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

summary(lm(lazy ~ condition * IRI1, data))
summary(lm(lazy ~ condition * IRI3, data))
summary(lm(lazy ~ condition * IRI5, data))

ggplot(data, aes(color = condition, y = as.numeric(lazy), x = IRI3)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("Patients' misfortunes do not usually disturb me a great deal.") +
  ylab("Patient Laziness") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

summary(lm(lazy ~ condition * as.numeric(insurance_1), data))
summary(lm(lazy ~ condition * as.numeric(yearsWork_1), data))
summary(lm(lazy ~ condition * as.numeric(ladder), data))
summary(lm(lazy ~ condition * as.numeric(income), data))
```

#### I feel like giving up 
```{r}
#| warning: false
#| message: false
#| code-fold: true
summary(lm(givingUp ~ condition * IRI2, data))
summary(lm(givingUp ~ condition * IRI4, data))
summary(lm(givingUp ~ condition * IRI6, data))

ggplot(data, aes(color = condition, y = as.numeric(givingUp), x = IRI4)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("If I'm sure I'm right about something, I don't \nwaste much time listening to patients’ arguments.") +
  ylab("Desire to Give Up on Patient") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

ggplot(data, aes(color = condition, y = as.numeric(givingUp), x = IRI6)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("When I'm frustrated with a patient, I usually try \nto put myself in his/her shoes for a while.") +
  ylab("Desire to Give Up on Patient") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

summary(lm(givingUp ~ condition * IRI1, data))
summary(lm(givingUp ~ condition * IRI3, data))
summary(lm(givingUp ~ condition * IRI5, data))

ggplot(data, aes(color = condition, y = as.numeric(givingUp), x = IRI1)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("I often have tender, concerned feelings for patients less fortunate than I am.") +
  ylab("Desire to Give Up on Patient") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

ggplot(data, aes(color = condition, y = as.numeric(givingUp), x = IRI3)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("Patients' misfortunes do not usually disturb me a great deal.") +
  ylab("Patient Honesty") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

ggplot(data, aes(color = condition, y = as.numeric(givingUp), x = IRI5)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("When I see a patient being taken advantage of,\n I feel kind of protective towards them.") +
  ylab("Patient Honesty") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

summary(lm(givingUp ~ condition * as.numeric(insurance_1), data))
summary(lm(givingUp ~ condition * as.numeric(yearsWork_1), data))
summary(lm(givingUp ~ condition * as.numeric(ladder), data))
summary(lm(givingUp ~ condition * as.numeric(income), data))
```

#### Patient not taking inititative
```{r}
#| warning: false
#| message: false
#| code-fold: true
t.test(as.numeric(data$initiative) ~ as.factor(data$condition))

ggplot(data, aes(x=condition, y=as.numeric(initiative))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
summary(lm(initiative ~ condition * IRI2, data))
summary(lm(initiative ~ condition * IRI4, data))
summary(lm(initiative ~ condition * IRI6, data))

summary(lm(initiative ~ condition * IRI1, data))
summary(lm(initiative ~ condition * IRI3, data))
summary(lm(initiative ~ condition * IRI5, data))

summary(lm(initiative ~ condition * as.numeric(insurance_1), data))
summary(lm(initiative ~ condition * as.numeric(yearsWork_1), data))
summary(lm(initiative ~ condition * as.numeric(ladder), data))
summary(lm(initiative ~ condition * as.numeric(income), data))
```

#### Patient is honest
```{r}
#| warning: false
#| message: false
#| code-fold: true
t.test(as.numeric(data$honest) ~ as.factor(data$condition))

ggplot(data, aes(x=condition, y=as.numeric(honest))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
summary(lm(honest ~ condition * IRI2, data))
summary(lm(honest ~ condition * IRI4, data))
summary(lm(honest ~ condition * IRI6, data))

ggplot(data, aes(color = condition, y = as.numeric(honest), x = IRI2)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("I sometimes try to understand my patients better by \nimagining how things look from their perspective.") +
  ylab("Patient Honesty") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

ggplot(data, aes(color = condition, y = as.numeric(honest), x = IRI4)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("If I'm sure I'm right about something, I don't \nwaste much time listening to patients’ arguments.") +
  ylab("Patient Honesty") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

ggplot(data, aes(color = condition, y = as.numeric(honest), x = IRI6)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("When I'm frustrated with a patient, I usually try \nto put myself in his/her shoes for a while.") +
  ylab("Patient Honesty") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

summary(lm(honest ~ condition * IRI1, data))
summary(lm(honest ~ condition * IRI3, data))
summary(lm(honest ~ condition * IRI5, data))

ggplot(data, aes(color = condition, y = as.numeric(honest), x = IRI1)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("I often have tender, concerned feelings for patients less fortunate than I am.") +
  ylab("Patient Honesty") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

ggplot(data, aes(color = condition, y = as.numeric(honest), x = IRI3)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("Patients' misfortunes do not usually disturb me a great deal.") +
  ylab("Patient Honesty") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

summary(lm(honest ~ condition * as.numeric(insurance_1), data))
summary(lm(honest ~ condition * as.numeric(yearsWork_1), data))
summary(lm(honest ~ condition * as.numeric(ladder), data))
summary(lm(honest ~ condition * as.numeric(income), data))

ggplot(data, aes(color = condition, y = as.numeric(honest), x = as.numeric(income))) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("Household Income") +
  ylab("Patient Honesty") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")
```

#### Patient is motivated
```{r}
#| warning: false
#| message: false
#| code-fold: true
t.test(as.numeric(data$motivated) ~ as.factor(data$condition))

ggplot(data, aes(x=condition, y=as.numeric(motivated))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
summary(lm(motivated ~ condition * IRI2, data))
summary(lm(motivated ~ condition * IRI4, data))
summary(lm(motivated ~ condition * IRI6, data))

ggplot(data, aes(color = condition, y = as.numeric(motivated), x = IRI4)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("If I'm sure I'm right about something, I don't \nwaste much time listening to patients’ arguments.") +
  ylab("Patient Motivation") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

summary(lm(motivated ~ condition * IRI1, data))
summary(lm(motivated ~ condition * IRI3, data))
summary(lm(motivated ~ condition * IRI5, data))

ggplot(data, aes(color = condition, y = as.numeric(motivated), x = IRI1)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("I often have tender, concerned feelings for patients less fortunate than I am.") +
  ylab("Patient Motivation") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

ggplot(data, aes(color = condition, y = as.numeric(motivated), x = IRI3)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("Patients' misfortunes do not usually disturb me a great deal.") +
  ylab("Patient Motivation") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

summary(lm(motivated ~ condition * as.numeric(insurance_1), data))
summary(lm(motivated ~ condition * as.numeric(yearsWork_1), data))
summary(lm(motivated ~ condition * as.numeric(ladder), data))
summary(lm(motivated ~ condition * as.numeric(income), data))

ggplot(data, aes(color = condition, y = as.numeric(motivated), x = as.numeric(income))) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("Household Income") +
  ylab("Patient Motivation") +
  expand_limits(y=c(1,5), x=c(1,7)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")
```

#### Important to me that patient improves
```{r}
#| warning: false
#| message: false
#| code-fold: true
t.test(as.numeric(data$healthImproves) ~ as.factor(data$condition))

ggplot(data, aes(x=condition, y=as.numeric(healthImproves))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
summary(lm(healthImproves ~ condition * IRI2, data))
summary(lm(healthImproves ~ condition * IRI4, data))
summary(lm(healthImproves ~ condition * IRI6, data))

ggplot(data, aes(color = condition, y = as.numeric(healthImproves), x = IRI4)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("If I'm sure I'm right about something, I don't \nwaste much time listening to patients’ arguments.") +
  ylab("Important to me that patient's health improves") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

ggplot(data, aes(color = condition, y = as.numeric(healthImproves), x = IRI6)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("When I'm frustrated with a patient, I usually try \nto put myself in his/her shoes for a while.") +
  ylab("Important to me that patient's health improves") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

summary(lm(healthImproves ~ condition * IRI1, data))
summary(lm(healthImproves ~ condition * IRI3, data))
summary(lm(healthImproves ~ condition * IRI5, data))

ggplot(data, aes(color = condition, y = as.numeric(healthImproves), x = IRI1)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("I often have tender, concerned feelings for patients less fortunate than I am.") +
  ylab("Important to me that patient's health improves") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

ggplot(data, aes(color = condition, y = as.numeric(healthImproves), x = IRI5)) +
  stat_smooth(method = "lm", se = F, fullrange = T) + 
  xlab("When I see a patient being taken advantage of,\n I feel kind of protective towards them.") +
  ylab("Important to me that patient's health improves") +
  expand_limits(y=c(1,5), x=c(1,5)) +
  theme_bw() +
  scale_color_manual(values=c("#d9d9d9","#252525")) +
  labs(color = "Condition") +
  theme(legend.position="bottom")

summary(lm(healthImproves ~ condition * as.numeric(insurance_1), data))
summary(lm(healthImproves ~ condition * as.numeric(yearsWork_1), data))
summary(lm(healthImproves ~ condition * as.numeric(ladder), data))
summary(lm(healthImproves ~ condition * as.numeric(income), data))
```

#### Attributions for patient behavior
```{r}
#| warning: false
#| message: false
#| code-fold: true
t.test(as.numeric(data$attributions) ~ as.factor(data$condition))

ggplot(data, aes(x=condition, y=as.numeric(attributions))) +
  geom_bar(fun="mean", stat="summary", position="dodge") +
  expand_limits(y=c(1,5))
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
summary(lm(attributions ~ condition * IRI2, data))
summary(lm(attributions ~ condition * IRI4, data))
summary(lm(attributions ~ condition * IRI6, data))

summary(lm(attributions ~ condition * IRI1, data))
summary(lm(attributions ~ condition * IRI3, data))
summary(lm(attributions ~ condition * IRI5, data))

summary(lm(attributions ~ condition * as.numeric(insurance_1), data))
summary(lm(attributions ~ condition * as.numeric(yearsWork_1), data))
summary(lm(attributions ~ condition * as.numeric(ladder), data))
summary(lm(attributions ~ condition * as.numeric(income), data))
```

:::

## Before Intervention

::: {.panel-tabset}

### IRI
```{r}
#| warning: false
#| message: false
#| code-fold: true
data <- data %>% 
  mutate_at(c("IRI1", "IRI3", "IRI5", "IRI2", "IRI4", "IRI6"), as.numeric)

keys.list <- list(IRI_EC = c('IRI1', '-IRI3', 'IRI5'),
                  IRI_PT = c('IRI2', '-IRI4', 'IRI6'))

scores <- scoreItems(keys.list, data, min = 1, max = 5)  
summary(scores, short = F)

data$IRI_EC = scoreItems(keys.list, data, min=1, max=5)$score[,1] 
data$IRI_PT = scoreItems(keys.list, data, min=1, max=5)$score[,2]
```

## Values
```{r}
#| warning: false
#| message: false
#| code-fold: true
data$valuesTreatment
data$valuesControl
```

:::