---
title: "01-Analyses"
subtitle: "Control Condition Pilot"
format:
  html:
    self-contained: true
    toc: true
editor: visual
editor_options: 
  chunk_output_type: console
---

# Description

These analyses were conducted as a pilot test of the control condition for Chapter 2 of my dissertation.

# Set-up

```{r}
#| warning: false
#| message: false
#| include: false
library(tidyverse)
library(psych)
library(lme4)
library(knitr)
library(sjPlot)
```

```{r}
#| warning: false
#| message: false
#| include: false
theme_perez <- function() {
    ggplot2::theme_bw() +
    ggplot2::theme(
      axis.text = element_text(colour = "black",  family = "Times New Roman", size = 12),
    axis.title = element_text(colour = "black", family = "Times New Roman", size = 13),
    legend.title = element_text(colour = "black", family = "Times New Roman", size = 13),
    legend.text = element_text(colour = "black", family = "Times New Roman", size = 12),
    plot.title = element_text(colour = "black", family = "Times New Roman", size = 13),
    plot.subtitle = element_text(colour = "black", family = "Times New Roman", size = 13)
      )
}

horzi_theme <- theme(    #   remove the gray background
  panel.background    = element_rect( size=.1, colour="black", fill="white") ,
  #   make the major gridlines light gray and thin
  panel.grid.major.y  = element_line( size=.1, colour="#666666" ) ,
  #   suppress the vertical grid lines
  panel.grid.major.x  = element_blank() ,
  #   suppress the minor grid lines
  panel.grid.minor    = element_blank() ,
  #   add axes
  axis.line           = element_line( size=.2 , colour="#666666" ),
  #   adjust the axis ticks
  axis.ticks          = element_line( size=.1 , colour="#666666" ),
  #   move the y-axis over to the left
  #axis.title.y        = element_text( angle=90, vjust=.5, hjust=.5 ),
  #   increase margin moved-over y-axis label fits
  # plot.margin = unit( c(.5,.25,.25,.5) , "in") ,
  title = element_text(  size=12 ) ,
  axis.title.x = element_text( size=12 ) ,
  axis.title.y = element_text( size=12 ) ,
  axis.text.x = element_text( size=12 ) ,
  axis.text.y = element_text( size=12 )
)

horzi <- horzi_theme

stat_sum_df <- function(fun, geom="crossbar", ...) {
  stat_summary(fun.data=fun, colour="black", geom=geom, width=.5,  ...)
}

# define the dodge object for equivalent error bar and geom_bar
dodge <- position_dodge(width=0.9)

# define a geom_bar
bars <- geom_bar(stat="summary", fun.y="mean", position="dodge")
```

## Data

### Quick Cleaning

```{r}
getwd()
#| warning: false
#| message: false
#| code-fold: true
data <- read.csv("Healthcare+Intervention+-+Control+Pilot+(SU24)_June+11,+2024_15.46.csv")

data <- data[-c(1:2),]
data <- data %>% 
  select(-c(1:7, 
            9:16,
            26:42,
            66:76,
            80:83))

data <- data %>% 
  select(-c(52:55))

write.csv(data, "Control-Pilot_Clean_Wide.csv")
```

```{r}
#| warning: false
#| message: false
#| code-fold: true
data$ResponseId <- as.factor(data$ResponseId)

longData <- 
  data %>%
  pivot_longer(
    cols = treatment_1:notes_2,
    names_to = c(".value", "strike"),
    names_sep = "_",
    values_drop_na = TRUE)

longData$strike <- as.factor(longData$strike)

write.csv(longData, "Control-Pilot_Clean_Long.csv")
```

# Findings TLDR

-   Doctors reported the issues in the control articles as being relevant to their experience.
-   Positive affect was higher (after reading articles) in active versus passive control.
-   Responses to the noncompliant patient in the scenario were slightly more negative after strike 1 for active control, but differences levelled out for strike 2.

```{r}
#| warning: false
#| message: false
#| code-fold: true
kable(table(data$Condition), col.names = c("Condition", "n"))
```

# Pre-Items

**To what extent do you agree that this is a big issue facing healthcare providers**

::: panel-tabset
#### Patient noncompliance

```{r}
#| warning: false
#| message: false
#| code-fold: true
data %>% 
  ggplot(aes(as.numeric(noncompliance))) +
  geom_density() +
  theme_classic() +
  labs(x = "Noncompliance",
       y = "Density") +
  expand_limits(x=c(1:6))

kable(psych::describe(as.numeric(data$noncompliance)), row.names = F)
```

#### Personnel issues

```{r}
#| warning: false
#| message: false
#| code-fold: true
data %>% 
  ggplot(aes(as.numeric(personnel))) +
  geom_density() +
  theme_classic() +
  labs(x = "Personnel",
       y = "Density") +
  expand_limits(x=c(1:6))

kable(psych::describe(as.numeric(data$personnel)), row.names = F)
```

#### Burnout

```{r}
#| warning: false
#| message: false
#| code-fold: true
data %>% 
  ggplot(aes(as.numeric(burnout))) +
  geom_density() +
  theme_classic() +
  labs(x = "Burnout",
       y = "Density") +
  expand_limits(x=c(1:6))

kable(psych::describe(as.numeric(data$burnout)), row.names = F)
```

#### Difficult patients

```{r}
#| warning: false
#| message: false
#| code-fold: true
data %>% 
  ggplot(aes(as.numeric(difficultPatients))) +
  geom_density() +
  theme_classic() +
  labs(x = "Difficult Patients",
       y = "Density") +
  expand_limits(x=c(1:6))

kable(psych::describe(as.numeric(data$difficultPatients)), row.names = F)
```
:::

# Manipulation Check

**How much do the articles reflect your experience as an HCP?**

```{r}
#| warning: false
#| message: false
#| code-fold: true
data <- data %>% 
  mutate(articleResponse = case_match(articleResponse, 
                                        "8" ~ 5,
                                        "9" ~ 6))
data %>% 
  ggplot(aes(as.numeric(articleResponse))) +
  geom_density() +
  theme_classic() +
  labs(x = "Article Accuracy",
       y = "Density") +
  expand_limits(x=c(1:6))

kable(psych::describe(as.numeric(data$articleResponse)), row.names = F)
```

# Affect

```{r}
#| warning: false
#| message: false
#| include: false
data$PANAS_pos <- as.numeric(data$PANAS_1) + as.numeric(data$PANAS_3) + as.numeric(data$PANAS_5) + as.numeric(data$PANAS_9) + as.numeric(data$PANAS_10) + as.numeric(data$PANAS_12) + as.numeric(data$PANAS_14) + as.numeric(data$PANAS_16) + as.numeric(data$PANAS_17) + as.numeric(data$PANAS_19)

data$PANAS_neg <- as.numeric(data$PANAS_2) + as.numeric(data$PANAS_4) + as.numeric(data$PANAS_6) + as.numeric(data$PANAS_7) + as.numeric(data$PANAS_8) + as.numeric(data$PANAS_11) + as.numeric(data$PANAS_13) + as.numeric(data$PANAS_15) + as.numeric(data$PANAS_18) + as.numeric(data$PANAS_20)
```

::: panel-tabset
#### Positive

```{r}
#| warning: false
#| message: false
#| code-fold: true
tab_model(t.test(data$PANAS_pos ~ data$Condition), pred.labels = "Positive Affect")

data %>% 
  filter(Condition != "") %>% 
  ggplot(aes(Condition, as.numeric(PANAS_pos))) +
  geom_bar(stat="summary", fun = "mean", position="dodge") +
  theme_classic() +
  labs(x = "Condition",
       y = "Positive Affect") +
  theme(legend.position = "bottom")
```

#### Negative

```{r}
#| warning: false
#| message: false
#| code-fold: true
tab_model(t.test(data$PANAS_neg ~ data$Condition), pred.labels = "Negative Affect")

data %>% 
  filter(Condition != "") %>% 
  ggplot(aes(Condition, as.numeric(PANAS_neg))) +
  geom_bar(stat="summary", fun = "mean", position="dodge") +
  theme_classic() +
  labs(x = "Condition",
       y = "Negative Affect") +
  theme(legend.position = "bottom")
```
:::

# Scenario

::: panel-tabset
#### First impression

**How severe is this patient's pain?**

```{r}
#| warning: false
#| message: false
#| code-fold: true
tab_model(t.test(as.numeric(data$severe) ~ data$Condition), pred.labels = "Pain Severity")

data %>% 
  filter(Condition != "") %>% 
  ggplot(aes(Condition, as.numeric(severe))) +
  geom_bar(stat="summary", fun = "mean", position="dodge") +
  expand_limits(y=c(1:10)) +
  scale_y_continuous(breaks=c(1:10)) +
  theme_classic() +
  labs(x = "Condition",
       y = "Pain Severity") +
  theme(legend.position = "bottom")
```

#### Frustration

**This is frustrating**

```{r}
#| warning: false
#| message: false
#| code-fold: true
longData %>% 
  filter(frustrating != "NA" & Condition != "") %>% 
ggplot(aes(Condition, as.numeric(frustrating))) +
  geom_bar(stat="summary", fun = "mean", position="dodge") +
    facet_wrap(~ strike) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  theme_classic() +
  labs(x = "Strike",
       y = "Frustration") +
  theme(legend.position = "bottom")

tab_model(t.test(as.numeric(data$frustrating_1) ~ data$Condition), title = "Strike 1", pred.labels = "Frustrating")

tab_model(t.test(as.numeric(data$frustrating_2) ~ data$Condition), title = "Strike 2", pred.labels = "Frustrating")
```

#### Lazy

**This patient is lazy**

```{r}
#| warning: false
#| message: false
#| code-fold: true
longData %>% 
  filter(lazy != "NA" & Condition != "") %>% 
ggplot(aes(as.factor(Condition), as.numeric(lazy))) +
  geom_bar(stat="summary", fun = "mean", position="dodge") +
      facet_wrap(~ strike) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  theme_classic() +
  labs(x = "Strike",
       y = "Lazy") +
  theme(legend.position = "bottom")

tab_model(t.test(as.numeric(data$lazy_1) ~ data$Condition), title = "Strike 1", pred.labels = "Lazy")
tab_model(t.test(as.numeric(data$lazy_2) ~ data$Condition), title = "Strike 2", pred.labels = "Lazy")
```

#### Honesty

**This patient is honest**

```{r}
#| warning: false
#| message: false
#| code-fold: true
longData %>% 
  filter(honest != "NA" & Condition != "") %>% 
ggplot(aes(as.factor(Condition), as.numeric(honest))) +
  geom_bar(stat="summary", fun = "mean", position="dodge") +
      facet_wrap(~ strike) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  theme_classic() +
  labs(x = "Strike",
       y = "Honest") +
  theme(legend.position = "bottom")

tab_model(t.test(as.numeric(data$honest_1) ~ data$Condition), title = "Strike 1", pred.labels = "Honest")
tab_model(t.test(as.numeric(data$honest_2) ~ data$Condition), title = "Strike 2", pred.labels = "Honest")
```

#### Exaggerating Pain

**This patient is exaggerating their pain**

```{r}
#| warning: false
#| message: false
#| code-fold: true
longData %>% 
  filter(exaggerate != "NA" & Condition != "") %>% 
ggplot(aes(as.factor(Condition), as.numeric(exaggerate))) +
  geom_bar(stat="summary", fun = "mean", position="dodge") +
      facet_wrap(~ strike) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  theme_classic() +
  labs(x = "Strike",
       y = "Exaggerating Pain") +
  theme(legend.position = "bottom")

tab_model(t.test(as.numeric(data$exaggerate_1) ~ data$Condition), title = "Strike 1", pred.labels = "Exaggerating Pain")
tab_model(t.test(as.numeric(data$exaggerate_2) ~ data$Condition), title = "Strike 2", pred.labels = "Exaggerating Pain")
```

#### Giving Up

**I feel like giving up on this patient**

```{r}
#| warning: false
#| message: false
#| code-fold: true
longData %>% 
  filter(givingUp != "NA" & Condition != "") %>% 
ggplot(aes(as.factor(Condition), as.numeric(givingUp))) +
  geom_bar(stat="summary", fun = "mean", position="dodge") +
      facet_wrap(~ strike) +
  expand_limits(y=c(1:5)) +
  scale_y_continuous(breaks=c(1:5)) +
  theme_classic() +
  labs(x = "Strike",
       y = "Give Up on Patient") +
  theme(legend.position = "bottom")

tab_model(t.test(as.numeric(data$givingUp_1) ~ data$Condition), title = "Strike 1", pred.labels = "Desire to Give Up")
tab_model(t.test(as.numeric(data$givingUp_2) ~ data$Condition), title = "Strike 2", pred.labels = "Desire to Give Up")
```
:::
